A performance comparison of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-25 latex/paper.tex
Worked on histogram results

In figure~\ref{fig:histo_tt_block} 
%TODO

@@

\subsection{Histogram: Gantt chart}

@@

\subsection{Histogram (NumPy): Number of blocks}
Figure~\ref{fig:histo_np_ms_block} shows the makespan of the application for
different block size. Note that the workers can process up to 64 tasks in paralle thus
they are not used at full capacity with 30 blocks. Overall, there is no substantial
difference for all engines and block size.

In figure~\ref{fig:histo_np_tt_block}, shows the total time spent in each function.
Again, the overhead for 30 blocks is erroneous due a lower amount of task than thread
which result in higher overhead for thread based engines. Considering the overhead
error and that at 30 blocks the worker only use half their core, the  total time is
substantially the same for all block size. This is due lower block sizes having a
lower IO time, however, it is balanced by the resulting increase in overhead.

@@

\subsection{Histogram (NumPy): Gantt chart}

>>>>

In figure~\ref{fig:histo_tt_block} the total time for each function is shown.
Note that at 30 blocks the worker's resources are not fully used since the workers
can process up to 64 task in parallel. Moreover, the overhead for 30 blocks is
erroneous due to a lower amount of block than available threads. This leads to thread
based engines to have higher overhead. Given that,

Spark has a much lower compute time which makes it significantly faster than Dask
engines. Overall, for all engines, lower block size results in lower IO time but
increased overhead time. Again, this is due to the overhead desynchronizing task thus
reducing the NFS bottle neck.
%TODO

@@

\subsection{Histogram: Gantt chart}
Figure~\ref{fig:histo_gantt} shows the Gantt chart of the baseline Histogram
experiment. Spark overhead is distributed through all the execution while Bag
overhead happens mostly when a thread read subsequent blocks and Delayed overhead is
concentrated after reading all the blocks.

The reduce is done differently on the engines. While Spark and Delayed compute all
the reduce task on one process (thread) Spark computes it on the driver process. On
the other hand, Bag computes the reduce tasks on different workers and sends the
informations to the driver process afterwards.

@@

\subsection{Histogram (NumPy): Number of blocks}
Figure~\ref{fig:histo_np_ms_block} shows the makespan of the application for
different block size. Note that the workers can process up to 64 tasks in parallel thus
they are not used at full capacity with 30 blocks. Overall, there is no substantial
difference for all engines and block size.

In figure~\ref{fig:histo_np_tt_block}, shows the total time spent in each function.
Again, the overhead for 30 blocks is erroneous due a lower amount of task than
available thread which result in higher overhead for thread based engines.
Considering the overhead error and that at 30 blocks the worker only use half their
core, the total time is substantially the same for all block size. This is due lower
block sizes having a lower IO time, however, it is balanced by the resulting increase
in overhead.

@@

\subsection{Histogram (NumPy): Gantt chart}
Figure~\ref{fig:histo_np_gantt} shows the Gantt chart of the baseline Histogram
(NumPy) experiment. The overhead for Spark and Bag is mostly located between a read
and compute task or compute and read task. On the other hand, Delayed overhead is
dispersed between all type of tasks. This cause Delayed to overlap more compute and
read tasks amongs the different workers.

In figure~\ref{fig:histo_np_gantt}, The read tasks of all engines are similar initially, however, when computation starts
the subsequent read tasks are much shorter. This is because read tasks for Delayed
become desynchronized hence it significanlty reduces the IO bottle neck.
